
\chapter{Introduction}

\section{Overview of \dispare}

\dispare is a system for \underline{dis}crete \underline{par}allel
\underline{e}vent simulation.  Unlike other simulation systems which
require the user to learn a ``simulation language,'' \dispare takes
standard C language code as input, augmented with a few
special constructs for specifying information about events.

\dispare accepts a ``specification file'' and various code files from
the user which describe the various kinds of events and contain code
to schedule their interactions.  From these files, \dispare builds a
complete, commented, source-level Chare Kernel (see below) program
capable of performing the specified simulation.  The user then compiles
the Chare Kernel code locally, modifying it at the source level if
desired, and executes it to perform the actual simulation.

\section{About The Chare Kernel}

The Chare Kernel is a machine-independent, message-passing parallel
programming system developed under the direction of L.V. Kal\'e at the
University of Illinois, Dept. of Computer Science.  Under the Chare
Kernel, various ``chares'' (akin to processes), written in a C
superset language, can execute simultaneously and send messages to one
another, making the system a good platform for discrete parallel event
simulation.

A technical description of how \dispare is implemented on the Chare
Kernel is found in Chapter \ref{technical}.  For specific information
about Chare Kernel programming, the reader is referred to the {\em Chare
Kernel Programming Language Manual}.

\section{\dispare Installation}

Create a directory, in some convenient location, where the \dispare
source files can reside.  These files are never modified once installed,
so the installer script changes the protection on them accordingly.

Once the directory is created, go to the directory in which the \dispare
files currently reside, and type {\tt INSTALL} {\em directoryname},
where {\em directoryname} is the full pathname of the directory you just
created. 

The installer script will copy the files over and change a couple of
lines in the builder so that it knows where to find \dispare files.
\dispare is now ready to use.
